---
title: "Command Line"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F)
library(tidyverse)
library(readxl)
library(DT)
#install.packages("remotes")
#remotes::install_github("rstudio/fontawesome")
library(fontawesome)

f <- "./static/commands.xlsx"
```

---

# Operating System Commands

## General
[SS64](https://ss64.com/)<br>
Reference guide containing syntax and examples for the most prevalent computing commands (Database and Operating System).<br>

## Windows

### CMD
[Microsoft Docs](https://docs.microsoft.com/en-us/windows-server/administration/windows-commands/cmd)<br>
Command line syntax

**Syntax**: `cmd [/c|/k] [/s] [/q] [/d] [/a|/u] [/t:{<b><f> | <f>}] [/e:{on | off}] [/f:{on | off}] [/v:{on | off}] [<string>]`

**Multiple commands**: `"<command1>&&<command2>&&<command3>"`

#### Parameters
```{r cmd, echo=F}
t1 <- read_excel(f, sheet="windows-commands")
# Show all rows in table (no pagination)
datatable(t1, options=list(paging=FALSE), rownames=F)
```

### Powershell 

<div style="display:inline;">`r fa("hard-hat")` `r fa("hammer")` Under construction...</div>

---

## Linux

### Commands
```{r}
t2 <- read_excel(f, sheet="linux-commands")
# Show all rows in table (no pagination)
datatable(t2, options=list(paging=FALSE), rownames=F)
```

### File System
```{r, echo=F}
t3 <- read_excel(f, sheet="linux-filesystem")
# Show all rows in table (no pagination)
datatable(t3, options=list(paging=FALSE), rownames=F)
```

### Permissions

General syntax: `_rwxrwxrwx 1 owner group`<br>

`_ | rwx | rwx | rwx` <Special><Owner><Group><All Users>

`r` = Read<br>
`w` = Write<br>
`x` = Execute

`chown` = Change ownership<br>
`chmod` = Change permissions<br>

`sudo chown <user>:<group> <file>`

`sudo chown 664 <file>`

### Package Manager
```{r, echo=F}
t4 <- read_excel(f, sheet="linux-packages")
# Show all rows in table (no pagination)
datatable(t4, options=list(paging=FALSE), rownames=F)
```

---

# Database Commands

<div style="display:inline;">`r fa("hard-hat")` `r fa("hammer")` Under construction...</div>