---
title: "RStudio Reference"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F)
```

---

```{r pkgs, eval = F}
# Still need to figure out what this is actually doing
if (!require(librarian)){
  remotes::install_github("DesiQuintans/librarian")
  library(librarian)
}
shelf(
  # database
  DBI, RPostgres,
  # spatial
  ggmap, leaflet, 
  r-spatial/mapview,
  sf, sp,
  # tidyverse
  dplyr, purrr, readr, tibble, tidyr,
  # todo: use these
  # googledrive,
  # report
  DT, gt, htmltools, htmlwidgets, kableExtra, knitr, markdown, rmarkdown, shiny, webshot,
  # utility
  fs, glue, here, png, scales, stringr, urltools)
here <- here::here
```

# References

  - [R Markdown Basics](https://rmarkdown.rstudio.com/authoring_basics.html)
  - [R Markdown Reference Guide](https://bookdown.org/yihui/rmarkdown/)
  - [Flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/)
  - [Awesome public datasets](https://github.com/awesomedata/awesome-public-datasets)

---

# Languages

## R
```{r}
x <- 5 * 5
x
```


## SQL

There are a couple ways to connect to a database instance. These examples show how to connect to a local PostgreSQL instance, and how to use the connection information to query a database.

### Option 1
Create connection chunk, then call connection in each subsequent chunk.
```{r connSQL, class.source='fold-show'}
library(DBI)

pass <- readLines("../../pwd.txt")

db = dbConnect(
  RPostgres::Postgres(),
  dbname   = "personal",
  host     = "localhost",
  port     = 5432,
  user     = "cgrant",
  password = pass
)
```

```{sql, connection=db, eval=F}
select * from sleepdata
```

### Option 2
Set default connection in the setup chunk (pretend its the setup chunk).
```{r setup-v2, eval=F, class.source='fold-show'}
library(DBI)
db = dbConnect(
  RPostgres::Postgres(),
  dbname   = "personal",
  host     = "localhost",
  port     = 5432,
  user     = "cgrant",
  password = pass
)
knitr::opts_chunk$set(connection = "db")
```

Now you dont have to specify the connection for each chunk.
```{sql, eval=F}
select * from sleepdata
```


## Python

To use a Python engine, you need to call `library(reticulate)` [link](https://rstudio.github.io/reticulate/)
```{r, class.source='fold-show'}
# install.packages("reticulate")
library(reticulate)

# Use specific Python installation
# use_python("C:/Python37")

# Use conda environment
use_condaenv("dev")
```

Now you can run Python code
```{python, class.source='fold-show'}
x = 4 * 4
print(x)
```

You can import libraries as normal
```{python, class.source='fold-show'}
import pandas as pd

vals = {"col1": ['a', 'b', 'c', 'd'], "col2": [1, 10, 100, 1000]}
df = pd.DataFrame(vals)
print(df)
```

Access objects created within Python chunks from R using `py$<var>`
```{r, class.source='fold-show'}
library(DT)
datatable(py$df)
```

---

# Mapping
```{r include=F}
library(leaflet)
library(dplyr)
```

## Leaflet
Use the leaflet map below to explore.
```{r, class.source='fold-show'}
leaflet() %>% 
  setView(lng=-122.90486, lat=47.03576, zoom=16) %>% 
  addTiles() %>% 
  addMarkers(lng=-122.90486, lat=47.03576, popup="WA State Capitol")
```

---

# Databases
```{r, include=F}
## Load packages
library(DBI)
library(RPostgres)
library(here)
library(glue)
library(leaflet)
library(lwgeom)
library(dplyr)
library(ggplot2)
library(rmarkdown)
library(DT)
```

## Packages
* [DT::datatables - options](https://datatables.net/reference/option/)

## Connection
```{r dbconn, class.source='fold-show'}
pass <- readLines("../../pwd.txt")

conn <- DBI::dbConnect(
  RPostgres::Postgres(),
  dbname   = "personal",
  host     = "localhost",
  port     = 5432,
  user     = "cgrant",
  password = pass
)
```


## Query
```{r dbquery, class.source='fold-show'}
# tbls <- dbListTables(conn)
sql <- glue("SELECT * FROM sleepdata")
res <- dbGetQuery(conn, sql)
# cols <- names(res)

datatable(res, options=list(scrollX=T))
```


# Plots

## Steps
```{r steps}
plt1 <- ggplot(res, aes(x=start_time, y=steps)) +
  geom_line(color="red", size=1) +
  ylab("Steps") +
  xlab("Start Date")
plt1
```

## Sleep time
```{r sleeptime}
plt2 <- ggplot(res, aes(x=start_time, y=(seconds_asleep / 60) / 60)) +
  geom_line(color="purple", size=1) +
  ylab("Hours Asleep") +
  xlab("Start Date")
plt2
```

